---
title: "Analyses: OPT Study"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import Data

Import the data and add variable labels using the `labelled::set_variable_labels()` function.

```{r import}
# load libraries
library(gtsummary)
library(tidyverse)

# import data
df_opt <- readRDS(file = here::here("data", "df_opt.rds"))

# add variable labels

```

## Cohort Summary

Create a table summarizing patient baseline characteristics by randomization assignment.

```{r summary}

```

## Treatment Comparison

Create a table comparing the following outcomes by randomization group
  - rate of gestational age <= 37 weeks at birth
  - mean difference in gestational age at birth
  - mean difference in birth weight
  
Report the summary statistics for each randomization group, the mean/rate difference between each group, the confidence interval for the difference, and a comparative p-value.
  
```{r compare}

```

## Models

To understand heterogeneity in baseline risk of each of the outcomes, build the following regression models.
Using the patients in the control group only, build three regression models to predict gestational age <= 37 weeks, continuous gestational age, and continuous birth weight using patient baseline characteristics.
Summarize each model using the gtsummary package, and merge the results into a single table.

```{r model}

```

## Save

Save all results

```{r save}
save(
  # list result objects here to save them
  file = here::here("data", "results.RData")
)
```

